%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.11 (19/6/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[francais]{layout}
\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.90]{geometry} % Reduce document margins
\setlength{\hintscolumnwidth}{2.3cm} % Uncomment to change the width of the dates column
\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name
\setlength{\hoffset}{0.7cm}
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{14in}
\setlength{\headsep}{25pt}
%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Michael} % Your first name
\familyname{Arbel} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\address{25 Howland St, Fitzrovia}{London W1T 4JG
 \--- United Kingdom}
\mobile{+44 (0) 78 79 53 76 43}
\email{michael.n.arbel@gmail.com}
\homepage{https://michaelarbel.github.io}{}
%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}
\cventry{09-2016 \\ 09-2020}{Gatsby Computational Neuroscience Unit, PhD in Machine Learning}{}{}{UK}
{Adversarial metrics for unsupervised learning. Supervisor: Arthur Gretton} 
\cventry{09-2014\\08-2015}{École Normale Supérieure de Cachan, MSc in Computer Science}{MVA}{}{France}
{Graphical Models, Deep Neural Networks, Reinforcement Learning, Object Recognition.} % Arguments not required can be left empty
\cventry{09-2011\\08-2014}{École Polytechnique, Ingénieur de l'Ecole Polytechnique}{Mathematics and Physics}{}
{}{Statistical Learning \& Nonparametric Estimation, Operations Research, Stochastic Calculus}
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{Work experience}
\cventry{09-2017\\present}{Teaching Assistant}{UCL}{}{}{
- Probabilistic and Unsupervised Learning\\
- Advanced Topics in Machine Learning\\
- DeepMind/CSML Seminars: Help organizing weekly seminars on topics in Machine Learning.}
\cventry{10-2015\\09-2016}{Computer Vision Engineer}{Chronocam}{}{}{
Developed multi-target tracking algorithms for neuromorphic event-based cameras.}
\cventry{04-2015\\09-2015}{Graduate Student Researcher}{Data Team DI}{ENS Paris}{}{Studied the dynamics of recurrent networks that capture long-range dependencies in simple grammars. Supervisor: Stéphane Mallat.}
\cventry{04-2014\\06-2014}{Graduate Student Researcher}{ORFE}{Princeton University}{}{Proved an existence and uniqueness result for a class of mean field games with dependence on the control. Supervisor: René Carmona. }
\section{Publications}

\cvitem{2018}{\textbf{Michael Arbel}, Arthur Gretton. Kernel Conditional Exponential Family. \textit{Proceedings of the 21st International Conference on Artificial Intelligence and Statistics, AISTATS 2018} }

\cvitem{2018}{Dougal J. Sutherland, Heiko Strathmann, \textbf{Michael Arbel}, Arthur Gretton. Efficient and principled score estimation. \textit{Proceedings of the 21st International Conference on Artificial Intelligence and Statistics, AISTATS 2018} }

\cvitem{2018}{Mikołaj Bińkowski, Dougal J. Sutherland, \textbf{Michael Arbel}, Arthur Gretton. Demystifying MMD GANs. \textit{Submitted to ICLR 2018} }


\section{Competitions and Awards}
\cvitem{2011--2015}{French Government Eiffel Excellence Scholarship}
\cvitem{2014}{Award of Financial Risk Chair of École Polytechnique for the research internship}
\cvitem{2013}{Award for "Outstanding Position Paper" at Model United Nation, New York.}
\cvitem{2009}{Participation to International Mathematical Olympiads, Germany.}
%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------
\begin{minipage}[t]{0.6\textwidth}
\section{Computer Skills}
\cvitem{Basic}{HTML, SQL}
\cvitem{Intermediate}{Java, R, Lua}
\cvitem{Advanced}{Python, C++, Matlab, \LaTeX, Git}
\end{minipage}
%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------
\begin{minipage}[t]{0.5\textwidth}
\section{Languages}
\cvitemwithcomment{English}{Proficiency Level}{}
\cvitemwithcomment{French}{Mother tongue}{}
\cvitemwithcomment{Arabic}{Mother tongue}{}
\end{minipage}
%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------

\end{document}