%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.11 (19/6/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://  creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{banking} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

  
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[francais]{layout}
\usepackage{shellesc} % For \write18
\usepackage{filecontents} % Ensure we can manage local files

% Download the BibTeX file automatically (adjust URL)




\usepackage[scale=0.90]{geometry} % Reduce document margins
\setlength{\hintscolumnwidth}{2.3cm} %
% personal data
\name{Michael}{Arbel}
\title{{\huge Machine Learning Researcher}}                               
\address{655 Av. de l'Europe}{38330 Montbonnot-Saint-Martin}{France}
\email{michael.n.arbel@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{https://michaelarbel.github.io}                         % optional, remove / comment the line if not wanted

% Social icons
\social[linkedin]{https://www.linkedin.com/in/michael-arbel-0a38a655/}                        % optional, remove / comment the line if not wanted                          % optional, remove / comment the line if not wanted
\social[twitter]{https://x.com/MichaelArbel}                             % optional, remove / comment the line if not wanted
\social[github]{https://github.com/MichaelArbel}                              
\usepackage[defernumbers=true,style=numeric,maxbibnames=9,maxcitenames=1,uniquelist=true,backend=biber,giveninits=true,sorting=ydnt,doi=true,url=false]{biblatex} 
\addbibresource{https://haltools.inria.fr/Public/exportPubli.php?auteur_exp=Michael\%2CArbel&format_export=bibtex&langue=Anglais&CB_accent_latex=oui}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% END BLACK MAGIC
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% 


\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Academic positions}
\cventry{Since 2022}{Member of the Thoth team}{Researcher at Inria}{Grenoble, France}{}{}
\cventry{2021-2022}{Working with Julien Mairal on bilevel optimization}{Starting Research Fellow at Inria}{Grenoble, France}{}{}

\section{Education}
\cventry{2016-2021}{Under the supervision of Arthur Gretton}{PhD in Machine Learning, University College London}{London, UK}{\textit{No revisions}}{ 
Dissertation: Regularization and Optimization of Generative Adversarial Networks.} 
\cventry{2014-2015}{Machine learning and computer vision (MVA)}{M.S. in applied mathematics at École Normale Supérieure}{Cachan, France}{\textit{High honors}}{Master's thesis at École Normale Supérieure de Paris under the supervision of  Stéphane Mallat, 
\\Subject: Wavelet analysis of long-range dependencies in simple grammars.}
\cventry{2011-2014}{Minor in physics}{B.S. \& M.S. in applied mathematics at École Polytechnique}{Palaiseau, France}{ GPA: 3.93/4}{
Master thesis at Princeton University, under the supervision of René Carmona,\\
Subject: Mean field games with a dependence on the distribution of the  control.}

\section{Industrial positions}
\cventry{2015-2016}{Computer Vision for neuromorphic cameras}{Research Engineer at Prophesee}{Paris, France}{}{}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Grants and scholarships}
\cvitem{2024-2028}{Research grant from ANR for project BONSAI, \textbf{ 374K euros}.}
\cvitem{2021-2022}{Starting research grant from INRIA, \textbf{ 10K euros}. }
\cvitem{2016-2021}{Scholarship from Gatsby Computational Neuroscience Unit for the PhD program. 22K pounds/year}
\cvitem{2011-2014}{Scholarship from the Eiffel Excellence Scholarship program. 14K euros/year. }


\section{Honors and Awards}
\cvitem{2024}{Spotlight presentation at NeurIPS 2024. ~10\% of submitted papers.} 
\cvitem{2022}{Long Oral presentation at AISTATS 2022.  Top ~4\% of accepted papers.} 
\cvitem{2021}{Long Oral presentation at ICML 2021.  Top ~14\% of accepted papers.} 
\cvitem{2020}{Spotlight presentation at ICLR 2020. ~2\% of submitted papers.}                             
\cvitem{2018}{Best Poster Award at MSR AI Summer School 2018 for paper [5]. Cambridge.}                         
\cvitem{2014}{Award of the Financial Risk Chair of Polytechnique for the Master's thesis.}

\section{Services to the Community}
\subsection{Editorial Activities}
\cventry{2023}{Area chair}{ICLR 2023 and NeurIPS 2023}{}{}{}
\cventry{2020-present}{Editorial board}{Member of JMLR editorial board of reviewers.}{}{}{}
\cventry{2018-2021}{Reviewer}{NeurIPS (2018-2021), ICLR (2019-2021), ICML (2021).}{}{}{}
\subsection{Organization of scientific events}
\cventry{2017-2019}{DeepMind/CSML Seminars}{UCL}{London, UK}{}{
Weekly research seminars in Machine Learning with invited speakers from the UK and Europe. Annual budget: 5K pounds.
}






\subsection{Teaching graduate courses}

\cventry{2022-present}{Kernel methods for statistical learning }{ENS Paris-Saclay}{Saclay, France}{}{}
\cventry{2022-present}{Advanced kernel learning}{Universi\'{e} Grenoble Alpes}{Grenoble, France}{}{}
\cventry{2023-2024}{Intelligent systems}{Universi\'{e} Grenoble Alpes}{Grenoble, France}{}{}

\section{Software}
\cvitem{\href{https://github.com/inria-thoth/mlxp}{MLXP}}{Main author of the package MLXP for automatically launching/tracking/querying several machine learning experiments. MIT License.}
\cvitem{\href{https://github.com/MichaelArbel/GeneralizedEBM}{GEBM}}{Pytorch implementation of  Generalized EBMs. BSD 3-Clause License}
\cvitem{\href{https://github.com/MichaelArbel/OT-sync}{OT-sync}}{Pytorch implementation of the Measure synchronization on quaternion manifolds. BSD 3-Clause License}
\cvitem{\href{https://github.com/MichaelArbel/KWNG}{KWNG}}{Pytorch implementation of the optimizer. BSD 3-Clause License}
\cvitem{\href{https://github.com/MichaelArbel/MMD-gradient-flow}{MMDflow}}{Pytorch implementation of the noise-injection algorithm. BSD 3-Clause License}
\cvitem{\href{https://github.com/MichaelArbel/Scaled-MMD-GAN}{SMMD-GAN}}{Tensoflow implementation of scaled MMD-GAN. BSD 3-Clause License}


\section{Selected Invited Talks}


\subsection{Invited talks at conferences and workshops}

\cvitem{2023}{Bayes Comp. Levi, Finland.}

\cvitem{2023}{Conference in Mathematics and Image Analysis. Berlin, Germany.}

\cvitem{2022}{Learning and Optimization in Luminy workshop. Luminy, France.}
\cvitem{2022}{ELISE Theory Workshop on Machine Learning Fundamentals. EURECOM, Sophia Antipolis, France.}
\cvitem{2020}{Workshop on Functional Inference and Machine Intelligence, EURECOM.}
\cvitem{2019}{Amazon Research Days (Berlin, Germany).}
\cvitem{2019}{Workshop on Recent developments in kernel methods, 2019, UCL (London, UK).}
\cvitem{2019}{Deep Learning Theory Kickoff Meeting 2019, MPI (Leipzig, Germany).}
\cvitem{2018}{Cambridge-Tübingen workshop 2018 (Tenerife, Spain).}


\subsection{Seminars}

\cvitem{2021}{NYU Center for Data Science. (NY, USA) Remote.}

\cvitem{2021}{Instituto Superior Técnico, Lisbon, Portugal (Remote).}

\cvitem{2020}{The Alan Turing Institute (London, UK).}
\cvitem{2020}{Department of Statistics, University of Oxford (Oxford, UK).}
\cvitem{2019}{The Alan Turing Institute (London, UK).}
\cvitem{2018}{Google Developer Group Reading and Thames Valley (Reading, UK).}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Publications}
\nocite{*}
\printbibliography[heading=none,title=none]

%
%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------  

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
 
\end{document}